% !TEX root = ../report.tex

\newcommand{\bo}[1]{\textbf{#1}}

\chapter{Architecture evaluation}
\label{ch:evaluation}

In this chapter the architecture of the system will be evaluated. After taking architectural decisions and building the system the architects have to make sure that the patterns applied suit the architecture, especially the quality attributes and key drivers .%in terms of benefits and liablities.

\section{Key-Driver Validation}
% http://www.cs.rug.nl/paris/papers/ECSA07.pdf

\subsection*{Layers}
\subsection*{Service Layer}
The Service Layer pattern defines the boundary of the application using a layer of services to be used by clients. This increases the interoperability, since the set of operation offered by the service layer are available to many kinds of clients. \\
\textbf{Benefits \& Liabilities} ~
\begin{itemize}
\item[+] Interoperability 
\end{itemize}

\subsection*{Front-Controller}
\subsection*{Domain Model}
\subsection*{Broker}
The reliability of the system increases by the use of the Broker pattern. The pattern guarantees the delivery of messages to the destination. This guarantees that statistics are computed by a server in the compute cluster.
The modifiability of the system increases, since the brokers separate the messaging logic from the domain logic. This means that changes to the messaging logic do not affect the rest of the system.

The interoperability of the system increases as well, since the broker allow the system to interoperate with the servers in the compute cluster.

The broker pattern does however introduce a slight overhead, which reduces the performance.\\
\textbf{Benefits \& Liabilities} ~
\begin{itemize}
\item[+] Reliability
\item[+] Modifiability
\item[+] Interoperability
\item[$-$] Performance
\end{itemize}

\subsection*{Model View Controller}
\subsection*{Unit of Work}
The Unit of Work will significantly reduce the load on the database. The increased performance has a direct impact on the usability of the system. Faster processing will make the web interface of the system more responsive to the actions of the user, which increases the usability.

While the unit of work does introduce a delay before the change in the in-memory object is present in the representation in the database, this delay is very short and does not affect the functional correctness of the system or the reliability of its results.\\
\textbf{Benefits \& Liabilities} ~
\begin{itemize}
\item[+] Performance 
\item[+] Usability
\end{itemize}


\subsection*{Shared Repository} 
%Repositories are the single point where we hand off and fetch objects. It is also the boundary where communication with the storage starts and ends.
%Mediates between the domain and the data mapping layers using a collection-like interface for accessing domain objects.

\textit{Benefits} \\

The repository gives a lot more control over how the data is handled. The benefits are:
\begin{itemize}
\item Reduces code (and code complexity)
\item Increases performance
\item Separated domain and data layers, increasing flexibility and changeability
\end{itemize}

Performing analysis on the data also consists of executing complex queries on the data source. The database that executes these queries, however, might change. Or the system might decide to use multiple databases and data sources.
Using the Repository pattern, these changes can \underline{be made fast}. The repository also allows for \underline{multiple configurations} to exist. So an extra repository could be created for testing purposes, only using an in-memory database to increase the test execution speed. \\

\textit{} Liabilities : \\
\textbf{+ Reusability} because the data store is central \\
\textbf{+ Integrability} because the data store is central \\
\textbf{+ Maintainability} thanks to the Separation of concerns \\
\textbf{+ Modifiability/Changeability} thanks to the Separation of concerns\\

\clearpage1
\section{Requirements validation}
\label{sec:req-validation}
\input{8-evaluation/functional-reqs.tex}
\input{8-evaluation/non-functional-reqs.tex}

