%!TEX root = ../report.tex
\clearpage
\section{Stories and use-cases}

In this section the architectural significant ue-cae will be presented.

% Installation ?
% Collect and store energy consumption
% The End-Uer wants to display his bill ( to specific ? ) / his energy conumption
% Update ?
% Computation ? by Spark , Map/Reduce , DOES THE SYSTEM COMPUTE THE STATISTICS ONLY WHEN THE USER ASKS FOR PECIFIC STATITICS OR EVERYTIME ?



\textbf{The End user registration} \\
\textit{Number} : UC-1 \\
\textit{Goal} : The user has to register on the website to create his account.
\textit{Primary Actor }:  End-User \\
\textit{Precondition}: The website has the internal process to add an user to the database
\textit{Main Success Scenario }: \\
 1. The user acess the HEMS URL \\
 2. The user click on the " Sign up " Button \\
 3. The website display a regitration form requests the Fullname, Username, email adress and adress of the user.\\
 4. The system checks if the user isn't already in the database. \\
 5. If not the user is added in the database. \\
 6. The user receives a confirmation link on his email adress and clicks on it. \\ % or verification code ?
 7. The user is redirected to the HEMS webite. \\
\textit{Extensions} 1. The user isn't added to the system database. \\
1a. An error message is displayed " The regitration failed, do you want to try again Y/N? ".
1a. If yes Go to step 3.
%2. The user is already in the database.
\textit{Postcondition} : The account is created : the user get acces to his own Home Energy Monitor interface. \\

\textbf{Receive / Collect external energy data} \\% (out of scope ?) \\
\textit{Number}: UC-2 \\
\textit{Goal}: The sytem needs to receive energy data to make the analysis. \\
\textit{Primary Actor} : The system \\
\textit{Precondition}: The energy data is available. \\
\textit{Main Success Scenario}: \\ % what is the process ?
\textit{Extensions} \\
\textit{Post condition}: \\

\textbf{Store energy consumption}\\
\textit{Number} : UC-3 \\
\textit{Goal}: The system needs to store the energy data it just received. \\
\textit{Primary Actor}: System \\
\textit{Precondition} : 1. The system can receive the data. \\
2.The sytem has a database \\
\textit{Main Success Scenario} : 1. The data received is directly stored in the database. \\
\textit{Extensions} : The data isn't stored. % why ? \\
\textit{Post-condition}: The data is in the database.\\

\textbf{Display the next bill}\\
\textit{Number} : UC-4 \\
\textit{Goal}: The End-Uer wants to display the estimation of his next bill \\ 
\textit{Primary Actor}:  End-User \\
\textit{Pre-condition}: The user is registered in the database of the system.\\
\textit{Main Success scenario} : \\
1. The user gets acess to his interface by clicking on "Sign in" Button\\ % sign up ?
2. In the menu he clicks on the "Bill" button.\\
3. In the bill section the user chooses the "Next bill". \\ % the previous ones are alo available
\textit{Extensions} \\
% Authentification failed
\textit{Postcondition} : The bill is displayed.

\textbf{Display analysis, daily/weekly/monthly report}\\ % too generic ?
\textit{Number} : UC-5 \\
\textit{Goal}: The End-Uer wants to display several kind of analysis about hi energy consumption \\ 
\textit{Primary Actor}: End-User \\
\textit{Pre-condition}: The user is registered in the system.
\textit{Main Success scenario} : \\
1. The user gets acess to his interface by clicking on " Sign in " Button \\
2. In the menu he clicks on " Analyis- Chart " \\ 
3. The system computes/make the analysis. \\
\textit{Extensions} : The statistics aren't made. \\
\textit{Postcondition} : Charts with different item are displayed.

\textbf{Update}\\
\textit{Number}: UC-6 \\
\textit{Goal}: The sytem needs to update itself. \\
\textit{Primary Actor} : The system \\
\textit{Precondition}: \\
\textit{Main Success Scenario}: \\
\textit{Extensions} \\
\textit{Post condition}: \\

\textbf{Configuration} \\
\textit{Number}: UC-7\\
\textit{Goal}: The user must be able to configure the sytem with his own characteritics. \\
\textit{Primary Actor} : The user \\
\textit{Precondition}: The user is registered in the database of the system. \\
\textit{Main Success Scenario}: 1. On the dashboard/website the user clicks on the " Settings " button. \\
2. The user gets access to the Settings section with all the possibilities/internal sections for example :frequency of alert, adding new devices etc.\\
\textit{Extensions}:1. The system didn't take into account the information the user just added. \\
1a. An error mesage is displayed " Configuration failed, would you like to try again Y/N ? ". \\
If yes Go to step1. \\
\textit{Post condition}:The system is set with the user's characteritics of his home and preferences. \\