% !TEX root = ../report.tex
\section{Technical non-functional requirements}
In this section, the technical non-functional aspects that are important to the system are described.

\subsection{Usability}
The sytem will be hopefully used by a lot of people who don't necessarily have knowledge in the technology field so the Usability is an important requirement so the end-user can acces all the information he needs. \\

 	\begin{longtable}{L{0.1\textwidth} L{0.7\textwidth} L{0.1\textwidth}}
		\reqRow{US}{app}{An application is available for tablets and phone with those OS Windows Phone, Android, and iPhone.} \\
 		\reqRow{US}{basic-understanding}{The end-user needs maximum ten minutes to get a basic understanding of system features through the UI. }\\
 		\reqRow{US}{spa}{Every feature/major option of the system can be accessed through the home page (Single Page Application). }\\
		\bottomrule
	\end{longtable}

% Email The user can receive an email with the information he aked (for example etimate bill) once a month.
%Error message

\subsection{Reliability}
 	\begin{longtable}{L{0.1\textwidth} L{0.7\textwidth} L{0.1\textwidth}}
		\reqRow{RE}{error-margin}{A margin of error of $5\%$ in the energy measurements is tolerated.} \\
 		\reqRow{RE}{availability}{The system should be available $99.9\%$. of the time which means down for 44 minutes within 6 months.
 		$AV = \frac{\text{MTTF}}{\text{MTTF} + \text{MTTR}} = \frac{\text{6 months}}{\text{6 months }+\text{44 minutes}} = \frac{4380 \text{ hours}}{4380 + 12 \text{ hours}} = 99.9 \%$ 
 		}\\
 		\reqRow{RE}{downtime}{The system should be down for maximum ten minutes when the user installs a new release (version).}\\
		\bottomrule
	\end{longtable}

 	
\subsection{Security}
Ensuring the security for the system is a major issue so all the data needed for its good functioning remain protected and consistent. \\

 	\begin{longtable}{L{0.1\textwidth} L{0.7\textwidth} L{0.1\textwidth}}
		\reqRow{SEC}{login}{Each user is identified and has to log in in order to access his "Home Energy Monitor" account.} \\
 		\reqRow{SEC}{encryption}{The data stored in the database is encrypted.}\\
 		\reqRow{SEC}{https}{The connection from/to the system is encrypted using secure connection.}\\
		\bottomrule
	\end{longtable}

\subsection{Interoperability}

 	\begin{longtable}{L{0.1\textwidth} L{0.7\textwidth} L{0.1\textwidth}}
		\reqRow{INT}{interface}{The web interface of the system is available and functioning for 95\% of the browser market share.} \\
 		\reqRow{INT}{rest}{The system exposes a REST interface that allows different electricity usage sensors to submit the electricity usage data.}\\
		\bottomrule
	\end{longtable}
 

\subsection{Scalability} 

The system should make the increase in workload, resources and users easy to handle that's why the scalability its part of non functional requirements of the system.\\

 	\begin{longtable}{L{0.1\textwidth} L{0.7\textwidth} L{0.1\textwidth}}
		\reqRow{SCA}{user}{The system should still perform as efficiently as it is suppose to be when the number of users doubled.} \\
 		\reqRow{SCA}{device}{The system should still perform as efficiently as it is suppose to be when the number of devices doubled.}\\
		\bottomrule
	\end{longtable}