% !TEX root = ../report.tex
\section*{Authors}

\begin{tabular}{L{\tw{0.45}} L{\tw{0.45}}}
	\textbf{Name}        & \textbf{E-Mail}               \\ \toprule
	Putra, Guntur        & G.D.Putra@student.rug.nl      \\
	Fakambi, Aur\'{e}lie & A.Fakambi@student.rug.nl      \\
	Schaefers, Joris     & J.Schaefers@student.rug.nl    \\
	Menninga, Wouter     & W.G.Menninga@student.rug.nl   \\ 
\end{tabular}

\section*{Revision History}
\begin{longtable}{L{\tw{0.1}} L{\tw{0.2}} L{\tw{0.1}} L{\tw{0.5}}}
	\textbf{Version} & \textbf{Author}       & \textbf{Date} & \textbf{Description}                                                                                                                                                                                                       \\ \endhead	\toprule
				0.1 & Schaefers & 15-11-15 & Added a stakeholders section \\
					& Schaefers & 15-11-15 & Added a key drivers section \\
					& Putra		& 15-11-15 & Added Introduction and System context \\
					& Fakambi   & 15-11-15 & Added non-functional req. and risks \\
					& Menninga  & 15-11-15 & Added high-level and functional req. \\
					& Menninga  & 15-11-15 & Improvements to risks \\
				\midrule
				0.2 & Schaefers & 20-11-15 & Added an initial list of patterns with description\\
					& Schaefers & 22-11-15 & Improved the analysis chapter, partially restructured and expanded explanations\\
					& Menninga  & 21-11-15 & Improvements to High-level requirements \\
					& Menninga  & 21-11-15 & Improvements to Functional requirements \\
					& Menninga  & 21-11-15 & Added system context / elaborated model \\
					& Putra		& 22-11-15 & Added hardware architecture \\
					& Putra		& 22-11-15 & Edited introduction \\
					& Fakambi   & 22-11-15 & Use-cases \\
					& Menninga  & 22-11-15 & Expanded system context / elaborated model \\
					& Menninga  & 22-11-15 & Improvements to use-cases \\
				\midrule

				0.3 & Menninga  & 28-11-15 & Improved Unit of Work and Service Layer in ch. 3 \\
					& Menninga  & 29-11-15 & Changed key drivers \\
					& Menninga  & 29-11-15 & Added/modified Layers pattern ch. 3 \\
					& Menninga  & 29-11-15 & Added Unit of Work/Service Layer/Layers to ch.6 \\
					& Putra		& 29-11-15 & Edited introduction and hardware architecture \\
					& Putra		& 29-11-15 & Added MVC and Template View pattern in chapter analysis\\
					& Putra		& 29-11-15 & Added elaborated architecture of MVC and Template View pattern\\
					& Fakambi   & 29-11-15 & Improvements to the use cases \\
					& Fakambi   & 29-11-15 & Added the shared repository pattern \\
					& Menninga  & 29-11-15 & Improvements to Function req. and use cases\\
					& Menninga  & 29-11-15 & Improved the Elaborated Model \\
					& Schaefers & 29-11-15 & Updated the analysis chapter and added the front page pattern. Added the front page structure image to the software chapter \\

				 \midrule
				0.4 & Schaefers & 6-12-2015 & Restructured the software chapter\\
					& Schaefers & 6-12-2015 & Enhanced the software chapter. Added description and images for layer function interaction and data flow using pipes\\
					& Putra		& 5-12-15 & Updated introduction chapter \\
					& Putra		& 5-12-15 & Updated MVC diagram in software architecture chapter \\
					& Putra		& 6-12-15 & Improved Non-functional requirements \\
					& Putra		& 6-12-15 & Added system evolution \\
					& Putra		& 6-12-15 & Added Functional requirement evaluation \\
					& Putra		& 6-12-15 & Added Non-functional requirement evaluation \\
					& Putra		& 6-12-15 & Added illustration for MVC and Template View pattern \\
					& Menninga  & 3-12-15 & Improved stakeholder/keydrivers and added stakeholder concern matrix \\
					& Menninga  & 3-12-15 & Improved Service Layer pattern implications \\
					& Menninga  & 5-12-15 & Completed pattern fields in ch. 3 \\
					& Menninga  & 5-12-15 & Added interoperability NFRs \\
				 	& Fakambi   & 6-12-15 & Improvements use-cases  \\
				 	& Fakambi   & 6-12-15 & Shared Repository Pattern and work on evolution  \\
				 	& Menninga  & 6-12-15 & Improved arguments/alternatives Broker, Data Mapper, Domain Model ch. 3 \\
				 	& Menninga  & 6-12-15 & Added Use Case for creating alert \\
				 	& Menninga  & 6-12-15 & Added evaluation for Unit of Work, Broker, Layers and Service Layer \\
	\bottomrule
\end{longtable}